\chapter{The Factory Integration}
This part is about integrating The Factory inside of The ERP and benefiting from it alongside The
BPM.\\\\

When trying to integrate any project with our solutions, we will need to reconsider the business
processes involved in the business. As stated before the business processes involved
\begin{itemize}
    \item Manufacturing the products
    \item Warehousing
    \item Provide an online market to show the products and sell them
    \item Delivering the products to the customers
\end{itemize}
For each business process, we will need to rethink how to migrate it in The ERP and what module in
the ERP can be used in it.

\section{Manufacturing}

For Manufacturing the products and controlling the hardware, we will consider using the
Manufacturing and IOT modules. With the IOT module, we can control the IOT kit which we will
use to connect and control the hardware. And the Manufacturing module which will be used to check
for the materials and products to start manufacturing which in the prototype project resembles the
sorting process.
\section{Online Market}
The online market is working through the client mobile app to show the products to the user. The
module that can be used is the product manager module to show the products and offer the
customers a way to buy them.
\section{Warehousing}
The ERP doesn’t offer a physical place to be used for warehousing but it has warehousing module to
keep track of all the products in the warehouse that can be used to fulfill the need of the warehousing
for the Factory.
\section{Delivering}
The ERP doesn’t have any module that can accomplish this mission, but the ERP can be expanded by
users to add modules, that don’t already exist, to perform the required task (which, in this case, is
delivering orders to customers).
\section{Database}
Both The ERP and the Factory have their own database, so before we can completely use The ERP,
we will need to migrate the two databases.\\\\
We don’t offer tools for migrating the database so the users will have to find external tools for
database migration, but The BPM offers a way to migrate database by making workflows that will
read the tables from one database and writing to the other database but for large databases that will be
very hard and time-consuming. The Factory database is small enough for this way to work and
migrate the database using it.
\section{Executing Tasks}
As for executing the business tasks, like making a new order and having it checked by users before
proceeding, this will be The BPM task to create a workflow that will wait for the new order and make
a user task for the users to evaluate order and then checking the evaluation and deciding to proceed
with the order or not.


\chapter{ERP - BPM - Factory}
This integration will benefit users, as all the services that the ERP modules offer will now be available
to the users to use, and are now integrated with the business by the unified database.\\\\
Which means users can be benefitting from the CRM module to deal with the customers and help
keep in touch with them, the Accounting module to monitor company expenses and customers
expenses data, as well as the other modules with the advanced features that they offer.\\\\
Users will also benefit from having a unified system that controls the whole business.\\\\
These features come from The ERP alone, but when also considering The BPM, users will also have
more capability to monitor tasks and get a grasp of the processes run by The BPM to have the ability
to track errors and add optimization to their businesses.\\\\
The ERP besides The BPM will offer the users a way to automate different processes in an organized
and easy way to handle the company growth and help them get rid of system administration hassle by
using them on the cloud which will all lead to a managed and organized system with a successful
business.